Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-07-06 paper/paper.Rmd
slightly rephrase kmeans intro

The so-called "Spatial CV" method after [@russ2010; @brenning2012] and implemented in package \pkg{sperrorest} uses the coordinates of all observations to create clusters in the spatial domain.
$k$-means clustering, which belongs to the centroid-based clustering family, has been proposed as a clustering method.
To avoid confusion with other spatial partitioning methods, we refer to this as coordinate-based clustering, or as `spcv_coords` in \pkg{mlr3spatiotempcv}, instead of using the generic "Spatial CV" term.

>>>>

The so-called "Spatial CV" method after [@russ2010; @brenning2012] and implemented in package \pkg{sperrorest} uses the coordinates of all observations to create clusters in the spatial domain with the help of the $k$-means clustering algorithm.^[$k$-means clustering belongs to the centroid-based clustering family.]
To avoid confusion with other spatial partitioning methods, we refer to this as coordinate-based clustering, or as `spcv_coords` in \pkg{mlr3spatiotempcv}, instead of using the generic "Spatial CV" term.
